### 2019-06-05 doc/chapters/towards_verifying_addition.tex
updated titles

\chapter{Towards Verifying Addition with Zero}
\label{chap:verify_add}

@@

\section{Turn object Into case object}

@@

\section{Get Rid of Abstract Type Member}

@@

\section{Replace BigInt Constructor Argument With String Literal}

@@

\section{Get Rid of Special Generics}

@@

\section{Get Rid of Concret Type}

@@

This was a missing feature of Stainless that was fixed on Mai 28, 2019 with pull request \mypound470 on GitHub\footnote{\url{https://github.com/epfl-lara/stainless/pull/470}}.

\section{Replace BigInt \&-Function With Bound Check}
\label{sec:bound_check}

@@

\section{Extract Private Inner Classes}

@@

\section{Remove Second Parameter of require}

@@

\section{Rewrite BigInt Comparison with Long}

@@

\section{Write Specification for Verification}

@@

\section{Propagate require}

>>>>

\chapter{Towards Verifying the Addition with Zero Property}
\label{chap:verify_add}

@@

\section{Turning Object into Case Object}

@@

\section{Getting Rid of Abstract Type Member}

@@

\section{Replacing the BigInt Constructor Argument With A String Literal}

@@

\section{Getting Rid of Special Generics}

@@

\section{Getting Rid of Concrete Type}

@@

This was a missing feature of Stainless that was fixed on Mai 28, 2019 with pull request \mypound470 on GitHub\footnote{\url{https://github.com/epfl-lara/stainless/pull/470}}.
Now it should work without this change.

\section{Replacing the BigInt \&-Function With Bound Check}
\label{sec:bound_check}

@@

\section{Extracting Private Inner Classes}

@@

\section{Removeing Second Parameter of require}

@@

\section{Rewriting BigInt Comparison with Long}

@@

\section{Writing Specification for Verification}

@@

\section{Propagating require}
